---
title: "Untitled"
author: "Zachary M. Smith"
date: "September 23, 2018"
output: html_document
---

# Style Guide

Code style is more important than you may first imagine. Adopting a consistent style will make it easier for you and your collaborators to read and comprehend your code. Please review and in future R-code use Hadley Wickham's (http://style.tidyverse.org/index.html) style guide. As mentioned in Hadely Wickham's guide, his guide is adapted from Google's style guide (https://google.github.io/styleguide/Rguide.xml); therefore, there are many similarities. I do not want to recreate these style guides here, instead I want to highlight what I believe are some of the more important features.

## Names

File names, function names, and column names should not contain spaces. It is very easy to create a name with two subsequent spaces by mistake and very frustrating to later trouble shoot why your call to this name in your R code is returning an error. 

I use __snake case__, "snake_case", instead of "snake case" or "snakeCase;" the later, "snakeCase", is known as __camel case__. Many programmers use camel case but I find I make more typos when I use this naming scheme and in find snake case easier to read. __Please use snake case.__

### Object Names: Discriptive Suffix

For object names, I prefer a style similar to the one found in [Google's style guide](https://google.github.io/styleguide/Rguide.xml) but with a descriptive suffix. I cannot provide a reference to this style but at one point I adopted a descriptive suffix that describes the objects class (e.g., data frame = ".df", vector = ".vec", scalar = ".scal", list = ".lst", matrix = ".mat", and time series = ".ts"). I have found this simple naming scheme to be very helpful because I immediately know what the intended class of the object at any point that it is referenced in the script. This makes it easier to identify a bug if an object named "object.df" is represented in my RStudio Environment pane as a vector or list.

__Examples:__
```{r, eval=FALSE}
# Data Frame-------------------------------------------------------------------
my.df <- data.frame()

# Vector-----------------------------------------------------------------------
my.vec <- c("a", "b", "c")
my.scal <- "a"

my.vec <- c(1:3)
my.scal <- 1

# Matrix-----------------------------------------------------------------------
my.mat <- matrix()

# List-------------------------------------------------------------------------
my.lst <- list()

# Time Series------------------------------------------------------------------
my.ts <- ts()
```

## Spacing and Indenting

Please follow the spacing (http://style.tidyverse.org/syntax.html#spacing) and indenting (http://style.tidyverse.org/syntax.html#indenting) guide lines provided in Hadely Wickham's style guide. I find it very difficult to follow code that does not adhere to these guidelines.

The following "good" and "bad" examples will create the exact same data frame. However, the "good" example is much easier to read and interpret.

__Good Example:__
```{r}
good.df <- data.frame(
  alphabet = letters,
  square_root = sqrt(81),
  add = 1 + 1,
  subtract = 1 - 1,
  multiply = 2 * 2,
  divide = 2 / 2,
  power = 2^2
)
```

__Bad Example:__
```{r}
bad.df<-data.frame(alphabet=letters,square_root=sqrt(81),add=1+1,subtract=1-1,multiply=2*2,divide=2/2,power=2^2)
```
