---
title: "Untitled"
author: "Zachary M. Smith"
date: "February 23, 2019"
output: html_document
---

# Loops

## for loop

```{r}
for (i in c("a", "b", "c")){
  print(paste("This iteration represents", i))
}
```

## apply family

* __Link:__ https://www.datacamp.com/community/tutorials/r-tutorial-apply-family

These functions also perform loops but are a little bit more specific in how the loop is performed or how the output is returned relative to the `for` loop.

### apply

The `iris` data set will be used as an example. The `Species` column will be dropped from `iris` for this exercies and this object will be stored as `iris.df`.
```{r}
iris.df <- head(iris[, names(iris) != "Species"])
```

Apply a function by row. In this case, `sum()` by row.
```{r}
apply(iris.df, 1, sum)
```

Apply a function by column. In this case, `sum()` by column.
```{r}
apply(iris.df, 2, sum)
```

### lapply

`lapply()` loops through a vector or list and returns a list, hence the "L" in `lapply()`. Compare the output below to the for loop example. `lapply()` returns a list of strings that were printed in the for loop example.
```{r}
lapply(c("a", "b", "c"), function(i) {
  paste("This iteration represents", i)
})
```

Now compare the `apply()` example summing rows above to this `lapply()` call
```{r}
lapply(1:nrow(iris.df), function(i) {
  sum(iris.df[i, ])
})
```

Now compare the `apply()` example summing columns above to this `lapply()` call.
```{r}
lapply(1:ncol(iris.df), function(i) {
  sum(iris.df[, i])
})
```


### sapply


`sapply()` loops through a vector or list and returns a vector. Compare the output below to the similar `for()` loop and `lapply()` examples. `sapply()` returns a vector of strings that were printed in the `for()` loop example and the strings returned as a list in the `lapply()` example.
```{r}
sapply(c("a", "b", "c"), function(i) {
  paste("This iteration represents", i)
})
```

Now compare the `apply()` and `lapply()` examples summing rows above to this `sapply()` call.
```{r}
sapply(1:nrow(iris.df), function(i) {
  sum(iris.df[i, ])
})
```

Now compare the `apply()` and `lapply()` examples summing columns above to this `sapply()` call.
```{r}
sapply(1:ncol(iris.df), function(i) {
  sum(iris.df[, i])
})
```

