---
title: "Untitled"
author: "Zachary M. Smith"
date: "February 24, 2019"
output: html_document
---

# Data Structure Exercise Solutions

1. Store "one", "two", "three", "four", "five" as a vector object called "char.vec".
```{r}
char.vec <- c("one", "two", "three", "four", "five")
```

2. Extract just "three" from char.vec.
```{r}
char.vec[3]
```

3. Extract "two" and "four" from char.vec.
```{r}
char.vec[c(2, 4)]
```

4. Show two ways to extract "two", "three", and "four".
```{r}
char.vec[2:4]
char.vec[c(2, 3, 4)]
```

5. Import the file "zms_thesis-macro_2017-06-18.csv" from the folder "data" using a combination of `file.path()` and `read.csv()`. Wrap `read.csv()` within `head()`, which will only return the first 6 rows of the data frame. Store the data frame object as "taxa.df".
```{r}
taxa.df <- head(read.csv(file.path("data",
                              "zms_thesis-macro_2017-06-18.csv"),
                    stringsAsFactors = FALSE))
```

6. Show two ways to extract the column `final_id` from taxa.df.
```{r}
taxa.df$final_id

taxa.df[, "final_id"]
```

7. Extract the second row from taxa.df (final_id should be "chironomus").
```{r}
taxa.df[2, ]
```

8. Extract the fourth value from `final_id` in `taxa.df` (should be "paratanytarsus").
```{r}
taxa.df$final_id[4]
```

9. Subset `taxa.df` to only include rows related to taxa from the class "insecta".
```{r}
taxa.df[taxa.df$class == "insecta", ]
```

11. Subset `taxa.df` to only include rows with the genera "chironomus" and "polypedilum".
```{r}
taxa.df[taxa.df$genus %in% c("chironomus", "polypedilum"), ]
```

