---
title: "Untitled"
author: "Zachary M. Smith"
date: "February 24, 2019"
output: html_document
---


# dplyr Exercises

Load __dplyr__.
```{r}
suppressPackageStartupMessages(
  library(dplyr)
)
```

## Example Data

Import the example data. This data represents benthic macroinvertebrate data collected in the littoral zone of Onondaga, Otisco, and Cazenovia lakes 
```{r}
taxa.df <- file.path("data",
                     "zms_thesis-macro_2017-06-18.csv") %>% 
  read.csv(stringsAsFactors = FALSE)

DT::datatable(taxa.df, options = list(scrollX = TRUE))
```


1. Subset the data to only include the columns `lake, station_id, sample_number, order, family, count` and store the data frame as an object named "sub.df".

2. Change the  column names in `sub.df` from "count" and "family" to "abund" and "fam", respectively.

3. Subset `sub.df` to only include samples from Onondag Lake ("onon") and represent represent the first sample collected (see `sample_number`). Store this object as "onon.df".

4. Sum abundances (`abund`) within `onon.df` to remove duplicate instances of families (`fam`) per station (`station_id`). 
    + aggregate by `lake, station_id, order, fam`
    + keep `abund` as the summed column name

5. Aggregate by `station_id` within `onon.df` and find the total abundance (`abund`) per `station_id`. Store this column as "total" in `onon.df`.

6. Calculate the percentage of the sample each family (`fam`) composes per station (`station_id`).

