---
title: "Untitled"
author: "Zachary M. Smith"
date: "February 24, 2019"
output: html_document
---


# tidyr Exercise Solutions

Load __tidyr__ and __dplyr__.
```{r}
library(tidyr)
suppressPackageStartupMessages(
  library(dplyr)
)
```

## Example Data

Import the example data. This data represents benthic macroinvertebrate data collected in the littoral zone of Onondaga, Otisco, and Cazenovia lakes 
```{r}
onon1.df <- file.path("data",
                     "zms_thesis-macro_2017-06-18.csv") %>% 
  read.csv(stringsAsFactors = FALSE) %>% 
  filter(station_id == "onon_1") %>% 
  select(unique_id, final_id, count)

DT::datatable(onon1.df, options = list(scrollX = TRUE))
```

1. Make `onon1.df` represent `final_id` as the column headers and `count` represent the values in the rows.
    + Store the object as "wide.df"
    + make sure you fill blanks with zeros
```{r}
wide.df <- onon1.df %>% 
  spread(final_id, count, fill = 0)
```

2. Convert `wide.df` back to a long data format where the taxonomic column headers now represent a column titled "final_id" and the the values from the taxonomic columns are represented in a column titled "count".
```{r}
long.df <- wide.df %>% 
  gather(final_id, count, -unique_id)
```

3. Why is `long.df` not equivalent to `onon1.df`?
```{r}
identical(long.df, onon1.df)
```

4. Can you make data frame equivalent to `long.df` without the use of `spread()` and `gather()`?
    + Store the object as "new.df"
    + Make sure they are equivalent with the use of `identical()`
        + You will need to use `select(unique_id, final_id, count) %>% data.frame()` before calling `identical()`
```{r}
new.df <- onon1.df %>% 
  complete(final_id,
           nesting(unique_id),
           fill = list(count = 0)) %>% 
  select(unique_id, final_id, count) %>% 
  data.frame()
  
identical(new.df, long.df)
```



