---
title: "Untitled"
author: "Zachary M. Smith"
date: "February 24, 2019"
output: html_document
---


# ggplot2 Exercise Solutions

```{r}
library(ggplot2)

suppressPackageStartupMessages(
 library(dplyr) 
)

library(tidyr)
```

## Example Data

Import the example data. This data represents benthic macroinvertebrate data collected in the littoral zone of Onondaga, Otisco, and Cazenovia lakes.
```{r}
taxa.df <- file.path("data",
          "zms_thesis-macro_2017-06-18.csv") %>% 
  read.csv(stringsAsFactors = FALSE)
```

Preprocess `taxa.df` to just represent order-level taxonomic counts per sample. For more details about this process see the [summarize] section.
```{r}
ord.df <- taxa.df %>% 
  select(unique_id, station_id, lake, order, count) %>% 
  group_by(unique_id, station_id, lake, order) %>% 
  summarize(count = sum(count)) %>% 
  ungroup() %>% 
  group_by(station_id, lake, order) %>% 
  summarize(count = mean(count)) %>% 
  ungroup()
```
 
Calculate the percentage of each sample represented by a given order-level taxon and use `complete()` to fill in missing combinations.
```{r}
pct.df <- ord.df %>% 
  group_by(station_id) %>% 
  mutate(total = sum(count),
         percent = count / total * 100) %>% 
  ungroup() %>% 
  tidyr::complete(order,
                  nesting(station_id, lake, total),
                  fill = list(count = 0, percent = 0)) %>% 
  mutate(lake = factor(lake, levels = c("onon", "ot", "caz")))
```

Import environmental data associated with the taxonomic counts.
```{r}
env.df <- file.path("data",
                     "zms_thesis-env_2017-06-18.csv") %>% 
  read.csv(stringsAsFactors = FALSE) %>% 
  mutate(station_id = stringr::str_sub(unique_id, 1, -3)) %>% 
  select(-unique_id) %>% 
  distinct()
```

Join the `env.df` with `pct.df`.
```{r}
pct.df <- pct.df %>% 
  left_join(env.df, by = "station_id")
```

## Exercises 

1. The column `substrate` represents the dominant substrate type present at a sampling location. Make sure that in future plots `substrate` type will be plotted from smallest to largest size ("sand", "gravel", "coarsegravel", "cobble").
```{r}
pct.df <- pct.df %>% 
  mutate(substrate = factor(substrate, levels = c("sand", "gravel", "coarsegravel", "cobble")))
```

2. Create box and whisker plots of percent Diptera by substrate type.
    + How  can you just represent "diptera" from the `pct.df` data frame?
    + Which __ggplot2__ functions are necessary to create a box and whisker plot?
```{r}
pct.df %>% 
  filter(order == "diptera") %>% 
ggplot(aes(substrate, percent)) +
  geom_boxplot()
```

3. Create box and whisker plots of percent Amphipoda by substrate type.
    + How does this plot compare to the Diptera plot?
```{r}
pct.df %>% 
  filter(order == "amphipoda") %>% 
ggplot(aes(substrate, percent)) +
  geom_boxplot()
```


4. Can you create a single box and whisker plot showing "diptera" vs. "amphipoda" percentages per substrate category?
    + In examples from the [ggplot2] section, we saw that setting a `fill` or `color` parameter can group the data.
    + Is that pattern as clear as you thought is was above?
```{r}
pct.df %>% 
  filter(order %in% c("diptera", "amphipoda")) %>% 
ggplot(aes(substrate, percent, fill = order)) +
  geom_boxplot()
```

5. Can you create a scatter plot showing the percent of Diptera and Amphipoda against `substrate_size_d50`?
```{r}
pct.df %>% 
  filter(order %in% c("diptera", "amphipoda")) %>% 
ggplot(aes(substrate_size_d50, percent, color = order)) +
  geom_point()
```

6. Can you add a linear model to the scatter plot above?
```{r}
pct.df %>% 
  filter(order %in% c("diptera", "amphipoda")) %>% 
ggplot(aes(substrate_size_d50, percent, color = order)) +
  geom_point() +
  geom_smooth(method = "lm", formula = "y ~ x")
```

7. Can you add a LOESS model to the scatter plot above?
```{r}
pct.df %>% 
  filter(order %in% c("diptera", "amphipoda")) %>% 
ggplot(aes(substrate_size_d50, percent, color = order, fill = order)) +
  geom_point() +
  geom_smooth(method = "loess", formula = "y ~ x")
```